\thesistitle

### 2019-07-16 sections/clonerefactor.tex
Finished up the section

>>>>

For CloneRefactor, we used this conceptual method of removing duplicates, but did not directly implemented these equations. The main reason for this is the runtime overhead, as this process has to iterate over each existing clone class and each of their clone instances. For large projects with a lot of duplication this process has a significant impact on performance.

\subsubsection{Method of removing redundant clone classes}
\todo{Write this section}
